---
title: "Activity Mar. 23"
format: html
editor: visual
---

## 

1\)

```{r}
library(tidyverse)
prisons <- read.csv("Prison_Boundaries.csv")

```

2\) what happens when we create a vector with two types represented in it? Is there a hierarchy to these types?

```{r}
x4 <- c(2, "times", TRUE, 4)
```

-   character comes first and then "2" and then "times" and then "TRUE" and then "4". if you try to create a vector with all these types, it will change them to the most flexible type which is character (1st)

-   double is the next flexible type (2nd)

-   integer is next (3rd)

-   logical is last (4th)

3\) Use the + and mean() operations on the following vectors:

```{r}
x1 <- c(1, 2, 3, 4, 5)
x2 <- c("a", "b", "c", "d", "e")
x3 <- c(TRUE, FALSE, FALSE, TRUE, FALSE)

#x1 + x2
#x1 + x3
#x2 + x3

#mean(x3)
#mean(x2)
#mean(x1)

```

-   get an error for x1+x2 and x2+x3 but it worked for x1+x3

-   mean(x3) worked- got 0.4, mean(x2) gave an error, mean(x1) worked- got 3

4\) Using `sapply(prisons, typeof)`, identify which columns in the data frame have an improper data type

```{r}

sapply(prisons, typeof)

```

-   I think TELEPHONE may have an improper data type because it is character but i think it should be integer and ZIP4 is a bunch of -999's

5\) For two of these variables mentioned in Q4, correct the data type using prior code

```{r}
prisons|>
  as.integer(TELEPHONE)

```

```{r}
prisons[ ,]
  
```

-   I am trying to remove the -999 but I am not sure how

6\) Using the cheatsheet mentioned earlier, try out two different `lubridate` functions on the date/time column in the `prisons` dataset

```{r}
library(lubridate)

prisons <- 
  prisons |> 
  mutate(SOURCEDATE = ymd_hms(SOURCEDATE))

sapply(prisons, typeof)
```
