---
title: "Activity 1- mtcars"
format: html
editor: visual
---

```{r}
mtcars
nrow(mtcars)
```

1\.

-   Number of observations and variables

    -   there are 11 columns and 32 rows

-   What does each row represent?

    -   each row represents the information about the particular car

-   A categorical and numeric variable

    -   categorical:

        -   ordinal- mpg

        -   nominal- car type

    -   numeric:

        -   discrete- carb

        -   continuous- wt

-   Information about the dataset (hint: use the Help tab)

    -   the data is from a magazine called 1974 Motor Trend US that uses the aspects of the automobile design and the performance of 32 automobiles

2.  Think and write down all possible operations you would do inside an algebra class
    2.  PEMDAS
3.  Convert the following variable name into something descriptive in snake case:

```{r}
a <- round(pi, digits = 2)
```

```{r}
snake_case <- round(pi,digits = 2)
```

4.  Re-write this code such that we use the piping operators

```{r}
mean_of_dd|>
  select(mtcars, c(disp, drat)), mean)
```

#confused

5.  The functions below are commonly used on vectors:

```{r}
length()
unique()
sort()
paste()
```

length(): This helps find or set the length of vectors

unique(): This returns a vector but when it detects that there are multiple of the same elements/rows, it deletes them when they are returned

sort(): This sorts vectors into ascending or descending order depending on which one you ask it to do

paste(): This concatenates vectors when changed to a character
