---
title: "Activity 2/11"
format: html
editor: visual
---

```{r}
library(ggplot2)
housing <- read.csv("https://jericholawson.github.io/classes/sds192/s26/data/housing.csv")
```

Questions:

1.  Identify the number of observations and variables in this dataset.

    1.  there are 20640 rows and 10 columns

2.  Determine which variables are numerical and categorical.

    1.  numerical

        1.  discrete: housholds

        2.  continuous: population

    2.  categorical

        1.  numerical: total rooms

        2.  ordinal: median income

3.  Recreate the following plot you see below using the `housing` dataset and `ggplot2`.

```{r}
ggplot(data = housing,
       aes(x = ocean_proximity))+
  geom_bar()


```

4.  Using code from the last problem, add to your code such that you are able to generate the following image:

```{r}
ggplot(data = housing,
       aes(x = ocean_proximity,
           fill = ocean_proximity))+
  geom_bar()+
  scale_fill_manual(values = c("darkorange4","burlywood3","azure", "darkturquoise", "aquamarine4"))

```

5.  Recreate the following plot you see below using the `housing` dataset and `ggplot2`.

```{r}





```
